Effective Dynamic Models of Metabolic Networks

### 2016-03-08 Paper_v1.tex
Results General Model Update1

\begin{abstract}
Mathematical models of biochemical networks are useful tools to understand and ultimately predict how cells utilize nutrients to produce valuable products.
Modified version of the last paragraph of the introduction.

@@

\section{Results}

>>>>

\begin{abstract}
Mathematical models of biochemical networks are useful tools to understand and ultimately predict how cells utilize nutrients to produce valuable products.
Modified version of the last paragraph of the introduction. Mike made this change.

@@

\section{Results}
In the general case model, we demonstrated that the performance of the hybrid cybernetic model with FBA modes was equivalent to that of the elementary modes. In the proof of concept metabolic network consisting of 6 metabolites and 7 reactions (Fig. \ref{fig:model-fitting} A), METATOOL generated 6 elementary modes. FBA generated 3 possible modes (pathways) for the same metabolic network. Temporal profiles of the extracellular metabolites and artificial biomass concentration are presented for both the HCM FBA and HCM EM models (Fig. \ref {fig:model-fitting} B).  HCM FBA has 9 kinetic parameters whereas HCM EM has 15 kinetic parameters. The kinetic parameters of HCM FBA were varied to fit the concentration profiles of the HCM EM model.
